---
title: "Introduction to Twitter Data in R"
author: "Aditya Ranganath"
date: "12/6/2021"
output:
  html_document:
        toc: true
        toc_depth: 3
        toc_float: true
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preliminaries: Load Libraries and Log into Twitter

```{r, message=FALSE, warning=F}
library(rtweet)
library(httpuv)
library(tidyverse)
library(tidytext)
```

Make sure you're logged onto twitter in a web browser

# Extracting Data from the Twitter API via *rtweet* Package

## Extracting data by hashtag

```{r}
# Pull tweets with #ValentinesDay; returns 1000 most recent tweets; time by GMT
valentine_tweets<-search_tweets(q="#ValentinesDay", 
                                   n=1000,
                                   include_rts=FALSE,
                                   `-filter`="replies",
                                   lang="en")
```

```{r}
#prints "valentine_tweets"
valentine_tweets
```

## Extracting by multiple hashtags or keywords

### "And" conditions 

```{r}
# Pull tweets with #ValentinesDay AND #SinglesAwareness
valentinesday_AND_singlesawareness<-search_tweets(q="#ValentinesDay #SinglesAwareness", 
                                    n=1000,
                                    include_rts=FALSE,
                                    `-filter`="replies",
                                    lang="en")

```

```{r}
# prints "valentinesday_single"
valentinesday_AND_singlesawareness
```


### "Or" conditions 

```{r}
# Pull tweets with #ValentinesDay OR singlesday
valentinesday_OR_singlesawareness<-search_tweets(q="#ValentinesDay OR singlesday", 
                                                  n=1000,
                                                  include_rts=FALSE,
                                                  `-filter`="replies",
                                                  lang="en")

```


```{r}
# prints "valentinesday_OR_singlesawareness"
valentinesday_OR_singlesawareness
```

## Searching twitter handles and extracting tweet history

```{r}
#Pull tweets from an account (doesn't have same time constraints)
# Pull last 500 tweets from @VDay, a global activist movement to end violence against women that is associated with Valentine's day (note sometimes the query will return less than specified number due to deletions)
vday_tweets<-get_timeline("@VDay", n=500)
```

```{r}
# prints vday_tweets
vday_tweets
```

# Querying twitter datasets

## Querying ```vday_tweets``` to find the 10 tweets with most favorites

```{r}
# Extracts 10 most favorited tweets from "vday_tweets"
vday_tweets_most_favorites<-vday_tweets %>% 
                              slice_max(favorite_count, n=10)
```

```{r}
# prints "vday_tweets_most_favorites"
vday_tweets_most_favorites
```

## Querying ```vday_tweets``` to find the 10 tweets with most retweets

```{r}
# Extracts 10 most retweeted observations from "vday_tweets"
vday_tweets_most_retweeted<-vday_tweets %>% 
                              slice_max(retweet_count, n=10) %>% 
                              select(created_at, screen_name, text, retweet_count)
```


```{r}
# prints "vday_tweets_most_retweeted"
vday_tweets_most_retweeted
```


# Querying ```vday_tweets``` to find 5 most frequently shared links from vday_tweets

```{r}
# extracts table with 5 most frequently shared links from the @Vday handle
vday_links_top5<-vday_tweets %>% filter(!is.na(urls_expanded_url)) %>% 
                                      count(urls_expanded_url, sort = TRUE) %>% 
                                      rename(times_shared=n) %>% 
                                      slice_max(times_shared, n=5) %>%
                                      unnest(cols=urls_expanded_url)
                                                                            
```


```{r}
# prints "vday_links_top5"
vday_links_top5
```

## Query ```valentine_tweets``` to find the 5 handles that have most frequently used hashtag ValentinesDay

```{r}
# extracts handles that most frequently used #ValentinesDay
valentines_frequent_tweeters<-valentine_tweets %>% 
                              count(screen_name) %>% 
                              slice_max(n, n=5)
```

```{r}
# prints "valentines_frequent_tweeters"
valentines_frequent_tweeters
```

## Query ```valentine_tweets``` to find the 10 hashtags appearing most frequently in conjunction with hashtag ValentinesDay

```{r}
ValentinesDay_coinciding_hashtags<-valentine_tweets %>% 
                                    select(hashtags) %>% 
                                    unnest(hashtags) %>%
                                    mutate(hashtag_cleaned=str_to_lower(hashtags)) %>% 
                                    filter(hashtag_cleaned!="valentinesday") %>% 
                                    select(-hashtag_cleaned) %>% 
                                    count(hashtags) %>% 
                                    slice_max(n, n=10)
```


```{r}
ValentinesDay_coinciding_hashtags
```

# Visualizing Twitter data

## Using ```ggplot``` to visualize twitter data 

```{r}
# creates new column that adds #
CancelStudentDebt_coinciding_hashtags<-ValentinesDay_coinciding_hashtags %>% 
                                        mutate(hashtag=paste0("#", hashtags))
```


```{r}
# Makes inverted bar chart of "CancelStudentDebt_coinciding_hashtags"
coincident_hashtags_plot<-
  ggplot(CancelStudentDebt_coinciding_hashtags, aes(x=reorder(hashtag, n), y=n))+
    geom_bar(stat="identity")+
      coord_flip()+
      xlab("")+
      ylab("Frequency")+
      ggtitle("Hashtags Most Frequently Used Along With #ValentinesDay")+
      labs(caption = "Data Collected from Twitter REST API via rtweet")
```

```{r}
# prints "coincident_hashtags_plot"
coincident_hashtags_plot
```

## Using rtweet's visualization functions: time series

```{r}
# creates hourly time series of tweets with #ValentinesDay on February 17
ts_plot(valentine_tweets, by="hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets with #ValentinesDay",
       subtitle = paste0(format(min(valentine_tweets$created_at), "%d %B %Y"), 
                         " to ", 
                         format(max(valentine_tweets$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") +
  theme_minimal()
```

**Student Exercise: Select a hashtag, and make a visualization of the 15 most frequently along with your chosen hashtag**





